A Real-Time Sonar Simulator for Automatic Target Recognition

### 2019-05-11 Simulator/article.tex
2019-04-19
2019-04-22
2019-05-04
2019-05-09
2019-05-10

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
% pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={Optimal Window Design for the Low Complexity Adaptive Beamformer in Active Sonar Imaging},
% pdfsubject={},
% pdfauthor={Jo Inge Buskenes},
% pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
\ifCLASSINFOpdf
%    \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
   \usepackage[pdftex,
    final,                %Keep hyperlink stuff even when in draft mode
    breaklinks=true,      %Break links when necessary
    linktocpage=true,     %Enable link to page?
    linkcolor=black,  %Colour of links to labels within document
    citecolor=black,      %Colour of links to the biliography
    filecolor=red,        %Colour of links to local files
    pagecolor=black,        %Colour of links to other pages withing document
    urlcolor=Blue,        %Colour of the links to external URLs
    colorlinks=true,      %??
    plainpages=false,     %Store roman/arabic numbering differently to avoid
    bookmarksnumbered ]{hyperref}
% 
% \else
%    \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}%
\fi
%    \usepackage{breakurl}                        % Allows 'dvips' driver to break links

@@

@@

\newcommand\step[1]{\tikz[baseline=(char.base)]{%
            \node[shape=circle,draw,color=Green,shade,top color=black!5!white,bottom color=black!15!white,inner sep=.75pt] (char) {\color{Green}#1};}}
\newcommand\figstep[2]{\step{#1}\mbox{}\hfill\parbox[t]{.97\linewidth}{#2}}

\makeatletter
\let\@oldseccntformat\@seccntformat
\DeclareRobustCommand{\@seccntformat}[1]{%
  \def\temp@@a{#1}%
  \def\temp@@b{subsubsection}%
  \ifx\temp@@a\temp@@b
  \else
  \@oldseccntformat{#1}
  \fi
}
\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\parindent\step{\normalfont\arabic{subsubsection}}\enskip}{0ex plus 0.1ex minus 0.1ex}{0ex}{\normalfont\normalsize\itshape}}%
\makeatother

@@

\usepackage{multirow}
\usepackage{tabularx}
\usepackage{collcell}
\usepackage{booktabs}
\usepackage{calc}

@@

% The below line commands ensure proper fill color along with the booktabs package
% \specialrule[width]{abovespace}{belowspace}
\colorlet{tableheadcolor}{tabBlue}
\newlength\arulesep\setlength\arulesep{\aboverulesep}
\newlength\brulesep\setlength\brulesep{\belowrulesep}
\setlength{\aboverulesep}{0pt}
\setlength{\belowrulesep}{0pt}  
\newcommand\topline{\arrayrulecolor{black}\specialrule{\heavyrulewidth}{\arulesep}{0pt}%
            \arrayrulecolor{tableheadcolor}\specialrule{\brulesep}{0pt}{0pt}%
            \arrayrulecolor{black}}
\newcommand\midline{\arrayrulecolor{tableheadcolor}\specialrule{\arulesep}{0pt}{0pt}%
            \arrayrulecolor{black}\specialrule{\lightrulewidth}{0pt}{0pt}%
            \arrayrulecolor{white}\specialrule{\brulesep}{0pt}{0pt}%
            \arrayrulecolor{black}}
\newcommand\cmidline[2][]{\arrayrulecolor{tableheadcolor}\cmidrule[\arulesep]{#2}%
                        \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#2}%
                        \arrayrulecolor{tableheadcolor}\cmidrule[\brulesep]{#2}%
%                         \arrayrulecolor{tableheadcolor}\cmidrule[\belowrulesep]{#1}%
%                         \vspace{-\belowrulesep}
%                         \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#1}
%                         \arrayrulecolor{tableheadcolor}\cmidrule[\belowrulesep]{#1}%
%                        \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#1}%\specialrule{\lightrulewidth}{0pt}{0pt}%
%                        \arrayrulecolor{white}\cmidrule[0\belowrulesep]{#1}%
                        \arrayrulecolor{black}}
%\newcommand\cbmidline[1]{\arrayrulecolor{tableheadcolor}\cmidrule[0\aboverulesep]{#1}%
%                        \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#1}%\specialrule{\lightrulewidth}{0pt}{0pt}%
%                        \arrayrulecolor{white}\cmidrule[0\belowrulesep]{#1}%
%                        \arrayrulecolor{black}}
%\newlength\arulesep{}\setlength\arulesep{\aboverulesep}\addtolength\arulesep{\lightrulewidth}
%\newcommand\cmidline[1]{\arrayrulecolor{tableheadcolor}\specialrule{\aboverulesep}{0pt}{-\aboverulesep}%
%            \arrayrulecolor{black}\ule{#1}
%            \arrayrulecolor{tableheadcolor}\specialrule{\belowrulesep}{-\belowrulesep}{0pt}%
%            \arrayrulecolor{black}}
%\newlength\trulesep{}\setlength  \trulesep{\aboverulesep}
%                     \addtolength\trulesep{\lightrulewidth}
%                     \addtolength\trulesep{\belowrulesep}
%\newlength\brulesep{}\setlength  \brulesep{\lightrulewidth}
%                     \addtolength\brulesep{\belowrulesep}
%\newlength\mrulesep{}\setlength  \mrulesep{\aboverulesep}
%                     \addtolength\mrulesep{\belowrulesep}
%\newcommand*{\cmidline}[1]{\cmidrule(rl){#1}}%
%                      \arrayrulecolor{tableheadcolor}\specialrule{\trulesep}{0pt}{-\trulesep}\arrayrulecolor{black}
%                      \cmidrule(rl){#1}
%%                      \arrayrulecolor{white}\specialrule{0pt}{-\mrulesep}{0pt}%
%                      \arrayrulecolor{black}
%}

>>>>

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
% pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={Optimal Window Design for the Low Complexity Adaptive Beamformer in Active Sonar Imaging},
% pdfsubject={},
% pdfauthor={Jo Inge Buskenes},
% pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
\ifCLASSINFOpdf
%    \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
   \usepackage[pdftex,
    final,                %Keep hyperlink stuff even when in draft mode
    breaklinks=true,      %Break links when necessary
    linktocpage=true,     %Enable link to page?
    linkcolor=black,  %Colour of links to labels within document
    citecolor=black,      %Colour of links to the biliography
    filecolor=red,        %Colour of links to local files
    pagecolor=black,        %Colour of links to other pages withing document
    urlcolor=Blue,        %Colour of the links to external URLs
    colorlinks=true,      %??
    plainpages=false,     %Store roman/arabic numbering differently to avoid
    unicode=true,
    bookmarksopen=true,
%    bookmarksopenlevel=3,
    bookmarksnumbered=false ]{hyperref}
% 
% \else
%    \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}%
\fi
%    \usepackage{breakurl}                        % Allows 'dvips' driver to break links

@@

% Exotic orchids
% https://visme.co/blog/wp-content/uploads/2016/01/63-1024x512.jpg
%\definecolor{cDarkBlue}{HTML}{192e5b}
%\definecolor{cBlue}{HTML}{1d65a6}
%\definecolor{cLightBlue}{HTML}{73a2c0}
%\definecolor{cGreen}{HTML}{00743f}
%\definecolor{cYellow}{HTML}{f2a104}
%\colorlet{cBase}{cLightBlue}
%\colorlet{cBaseMark}{cGreen}
%\colorlet{cBrightText}{cYellow}
%\colorlet{cDarkText}{cDarkBlue}

%\definecolor{cBase}{HTML}{375e97}
% \colorlet{cBase}{yellow}
\colorlet{cBase}{tabBlue}
%\definecolor{cBaseMark}{HTML}{3f681c}
\colorlet{cBaseMark}{Green}
\definecolor{cDarkText}{HTML}{ff662f}
\definecolor{cBrightText}{HTML}{3492c2}
% \definecolor{cBrightText}{HTML}{2492c2}
% \definecolor{cDarkArrow}{HTML}{ff662f}
% \definecolor{cBrightArrow}{HTML}{3492c2}
\colorlet{cDarkArrow}{gray}
\colorlet{cBrightArrow}{gray}

\newcommand\supcarry[1]{{\color{cBrightText}#1}}
\newcommand\subcarry[1]{{\color{cDarkText}#1}}

@@

\newcommand\step[1]{\tikz[baseline=(char.base)]{%
            \node[shape=circle,draw,color=cBaseMark,shade,top color=black!5!white,bottom color=black!15!white,inner sep=.75pt] (char) {\color{cBaseMark}#1};}}
\newcommand\figstep[2]{\step{#1}\mbox{}\hfill\parbox[t]{.97\linewidth}{#2}}

\makeatletter
\let\@oldseccntformat\@seccntformat
\DeclareRobustCommand{\@seccntformat}[1]{%
  \def\temp@@a{#1}%
  \def\temp@@b{subsubsection}%
  \ifx\temp@@a\temp@@b
  \else
  \@oldseccntformat{#1}
  \fi
}
\let\oldsubsubsection\subsubsection
\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\parindent\step{\normalfont\arabic{subsubsection}}\enskip}{0ex plus 0.1ex minus 0.1ex}{0ex}{\normalfont\normalsize\itshape}}%
\makeatother

@@

\usepackage{multirow}
\usepackage{tabularx}
\usepackage{collcell}
\usepackage{booktabs}
\usepackage{calc}
%\usepackage{ifthen}

@@

%% Cool blues (sea)
%\definecolor{deep_aqua}{HTML}{003b46}
%\definecolor{ocean}{HTML}{07575b}
%\definecolor{wave}{HTML}{66a5ad}
%\definecolor{sea_foam}{HTML}{c4dfe6}
%\colorlet{base}{wave}
%\colorlet{bright}{ocean}
%\colorlet{dark}{deep_aqua}
%
%% Invigorating
%% https://visme.co/blog/wp-content/uploads/2016/01/26-1024x512.jpg
%\definecolor{cDarkBlue}{HTML}{003b46}
%\definecolor{cBlue}{HTML}{07575b}
%\definecolor{cLightBlue}{HTML}{66a5ad}
%\definecolor{cYellow}{HTML}{c4dfe6}
%\definecolor{cRed}{HTML}{c4dfe6}
%\colorlet{base}{wave}
%\colorlet{bright}{ocean}
%\colorlet{dark}{deep_aqua}

%% Invigorating
%% https://visme.co/blog/wp-content/uploads/2016/01/26-1024x512.jpg
%\definecolor{cBlue}{HTML}{80add7}
%\definecolor{cGreen}{HTML}{0abda0}
%\definecolor{cWhite}{HTML}{ebf2ea}
%\definecolor{cYellow}{HTML}{d4dca9}
%\definecolor{cBrown}{HTML}{bf9d7a}
%\colorlet{cBase}{cBlue}
%\colorlet{cBaseMark}{cGreen}
%\colorlet{cBrightText}{cYellow}
%\colorlet{cDarkText}{cBrown}

% The below line commands ensure proper fill color along with the booktabs package
% \specialrule[width]{abovespace}{belowspace}
\colorlet{tableheadcolor}{cBase}
\newlength\arulesep\setlength\arulesep{\aboverulesep}
\newlength\brulesep\setlength\brulesep{\belowrulesep}
\setlength{\aboverulesep}{0pt}
\setlength{\belowrulesep}{0pt}  
\newcommand\topline{\arrayrulecolor{black}\specialrule{\heavyrulewidth}{\arulesep}{0pt}%
            \arrayrulecolor{tableheadcolor}\specialrule{\brulesep}{0pt}{0pt}%
            \arrayrulecolor{black}}
\newcommand\midline{\arrayrulecolor{tableheadcolor}\specialrule{\arulesep}{0pt}{0pt}%
            \arrayrulecolor{black}\specialrule{\lightrulewidth}{0pt}{0pt}%
            \arrayrulecolor{white}\specialrule{\brulesep}{0pt}{0pt}%
            \arrayrulecolor{black}}
\newcommand\cmidline[2][]{\arrayrulecolor{tableheadcolor}\cmidrule[\arulesep]{#2}%
                        \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#2}%
                        \arrayrulecolor{tableheadcolor}\cmidrule[\brulesep]{#2}%
%                         \arrayrulecolor{tableheadcolor}\cmidrule[\belowrulesep]{#1}%
%                         \vspace{-\belowrulesep}
%                         \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#1}
%                         \arrayrulecolor{tableheadcolor}\cmidrule[\belowrulesep]{#1}%
%                        \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#1}%\specialrule{\lightrulewidth}{0pt}{0pt}%
%                        \arrayrulecolor{white}\cmidrule[0\belowrulesep]{#1}%
                        \arrayrulecolor{black}}
%\newcommand\cbmidline[1]{\arrayrulecolor{tableheadcolor}\cmidrule[0\aboverulesep]{#1}%
%                        \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#1}%\specialrule{\lightrulewidth}{0pt}{0pt}%
%                        \arrayrulecolor{white}\cmidrule[0\belowrulesep]{#1}%
%                        \arrayrulecolor{black}}
%\newlength\arulesep{}\setlength\arulesep{\aboverulesep}\addtolength\arulesep{\lightrulewidth}
%\newcommand\cmidline[1]{\arrayrulecolor{tableheadcolor}\specialrule{\aboverulesep}{0pt}{-\aboverulesep}%
%            \arrayrulecolor{black}\ule{#1}
%            \arrayrulecolor{tableheadcolor}\specialrule{\belowrulesep}{-\belowrulesep}{0pt}%
%            \arrayrulecolor{black}}
%\newlength\trulesep{}\setlength  \trulesep{\aboverulesep}
%                     \addtolength\trulesep{\lightrulewidth}
%                     \addtolength\trulesep{\belowrulesep}
%\newlength\brulesep{}\setlength  \brulesep{\lightrulewidth}
%                     \addtolength\brulesep{\belowrulesep}
%\newlength\mrulesep{}\setlength  \mrulesep{\aboverulesep}
%                     \addtolength\mrulesep{\belowrulesep}
%\newcommand*{\cmidline}[1]{\cmidrule(rl){#1}}%
%                      \arrayrulecolor{tableheadcolor}\specialrule{\trulesep}{0pt}{-\trulesep}\arrayrulecolor{black}
%                      \cmidrule(rl){#1}
%%                      \arrayrulecolor{white}\specialrule{0pt}{-\mrulesep}{0pt}%
%                      \arrayrulecolor{black}
%}
